Understanding the Impact of Mortgage State and Income on Household Poverty Status

### 2024-04-17 paper/paper.qmd
some edit

\newpage
# Introduction
Over the last few decades, the United States have implemented many policies, in an effort to address and mitigate poverty [@Kearney_Harris]. In 2019, the United States experienced the culmination of an economic expansion that followed the Great Recession. The poverty rate was estimated to be 10.5% in 2019 [@Semega_2022]. In order to reduce poverty further, it is important for us to analyze why some US household are in poverty in 2019. We analyze the 2019 Revised Supplemental Poverty Measure (SPM) Research dataset from the United States Census Bureau (USCB) [@Bureau_2022]. USCB is an agency of the U.S. Federal Statistical System, responsible for producing data about the American people and economy [@uscb]. Supplemental Poverty Measure was developed to address numerous concerns of official poverty measure critics, providing an improved statistical picture of poverty [@Gesumaria_2015]. We build a prediction model for households poverty status using 2019 Revised SPM dataset. We primarily look at two factors: mortgage status and income in each household. This allows us to look at the question whether potential financial factors may cause the poverty status for some US households in 2019.

@@

The intercept ($\alpha$) and coefficients ($\beta_1$, $\beta_2$) are assigned informative prior distributions to regularize the model. Specifically, we assume a normal distribution with a mean of 0 and a standard deviation of 2.5 for each parameter. Setting the prior to 0 assumes there is no poverty in any household regardless of their mortgage or income. Then, when we factor in real observations, we can see how things shift. If the distribution shifts left (less than 0), then we know that particular mortgage or income state is more likely to result in household poverty. This approach gives us a clear way to see how data affects the financial situation of households

>>>>

\newpage
# Introduction
Over the last few decades, despite many policies the United States have implemented to mitigate poverty, there has been no real improvement [@Kearney_Harris]. Poverty remains a major issue in the US, affecting millions of people. In 2019, the poverty rate was 10.5% [@Semega_2022]. Therefore, it is important to find out what are the causes of poverty, in order to reduce it. Multiple research, using the Official Poverty Measure, was conducted to look at why poverty persists. However, the Official Poverty Measure is flawed in various aspects, such as not accounting for regional differences in costs of living and government benefits  [@Gesumaria_2015]. So we will analyze why some US household are in poverty in 2019 using the 2019 Revised Supplemental Poverty Measure (SPM) Research dataset from the United States Census Bureau (USCB) [@Bureau_2022]. USCB is an agency of the U.S. Federal Statistical System, responsible for producing data about the American people and economy [@uscb]. Supplemental Poverty Measure was developed to address numerous concerns of Official Poverty Measure critics, providing an improved statistical picture of poverty [@Gesumaria_2015]. We build a prediction model for households poverty status using 2019 Revised SPM dataset. We primarily look at two factors: mortgage status and income in each household. This allows us to look at the question whether potential financial factors may cause the poverty status for US households in 2019.

@@

The intercept ($\alpha$) and coefficients ($\beta_1$, $\beta_2$) are assigned informative prior distributions to regularize the model. Specifically, we assume a normal distribution with a mean of 0 and a standard deviation of 2.5 for each parameter.
